Preregistration analysis, Cost 2 study

### 2019-05-16 Cost2/Cost2_prereg.Rmd
pre/post permutation tests

# get the coefficients and confidence intervals
# and concatenate
prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
```

>>>>

# get the coefficients and confidence intervals
# and concatenate
prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")

## PRE/POST PAIRED PERMUTATIONS
temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
  plyr::dlply("Cost", identity)

# paired perms and effect sizes
prepost$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
prepost$Perms <- sapply(temp, function(data) {permute(data$propAccept_1, data$propAccept_2, paired = T, simple = T)})
```
